What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Block
Bypassing CRAN restrictions wiht unlockBinding

\mypara{Block.} %injecting pre nad post processing

>>>>

\mypara{Block.} In package \emph{vglm}, \eval is used to inject a pre-processing code at the beginning of a function implementing a statistical model: 
\begin{lstlisting}
if (length(slot(family, "first"))) 
	eval(slot(family, "first"))
\end{lstlisting}

\mypara{Simple function calls.} This corresponds to minimized expression \c{F()}, \ie calls without nested functions and without variables (but possibly named arguments). For instance, package \emph{foreach} provides \c{foreach}-like loops. It makes it possible to initialize the iterator variables, with code \c{init}, which is equal \c{quote(list())} by default. \c{init} is then used to initialize the \c{foreach} accumulator \c{state\$accum <- eval(combineInfo\$init, envir=extra, enclos=obj\$evalenv)}.

A peculiar use of \eval is to bypass some checks performed to accept code submitted to CRAN. For example, bindings can be \emph{locked} in an environment, \ie forbidding its value to be modified. The binding can be unlocked though by calling \c{unlockBinding} but packages in CRAN are forbidden to use that function.  Package \emph{data.table} bypasses this restriction by building a call piece by piece, to unlock binding \c{.N}. The call is then evaluated.

\begin{lstlisting}
if (locked.N) eval(call("unlockBinding", ".N", parent.frame()))  
\end{lstlisting}
